Yeast RNA-seq 48 sample simulation study

### 2018-03-27 datasets/GWAS/GWAS.Rmd
Add plots for ash assumptions and covariate comparisons

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$ind_covariate <- mcols(sbN)$ind_covar_N
mcols(sbN)$tstat <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateHeatmap(sbN, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans="log1p")
covariateHeatmap(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 linePlot = TRUE, trans="log1p")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$ind_covariate <- abs(mcols(sbAF)$ind_covar_AF-0.5)
mcols(sbAF)$tstat <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateHeatmap(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans = "log1p")
covariateHeatmap(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25, 
                 linePlot = TRUE)
```

>>>>

## Check Assumptions for ash

We'll create a plot to examine the distribution of effect sizes, since
the ash method assumes that the distribution of true (unobserved) effect
sizes is unimodal.

```{r}
ggplot(data=bmi, aes(effect_size)) +
  geom_histogram(bins=30)
```

We'll also explore how the standard error (used by ash) 
correlates with the independent covariates (used by methods that incorporate 
covariates), in order to get an idea of how these pieces of information relate
to one another.

```{r}
ggplot(data=bmi, aes(x = ind_covar_N, y = SE)) +
  geom_hex(bins=125) +
  xlab("Covariate: Sample Size")

ggplot(data=bmi, aes(x = ind_covar_AF, y = SE)) +
  geom_hex(bins = 125)+
  xlab("Covariate: Minor allele frequency") 
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$effect_size <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateLinePlot(sbN, alpha=0.05, covname="effect_size", nbins=25, 
                 trans="log1p")
covariateLinePlot(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 trans="log1p")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$effect_size <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateLinePlot(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 trans = "log1p")
covariateLinePlot(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25)
```

### 2018-03-27 datasets/RNA-Seq/yeast-simulation.Rmd
Add plots for ash assumptions and covariate comparisons

```{r, results='hide', message=FALSE}
# Load packages and source benchmark FDR
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)

@@

Check unimodal assumption (for ash).

```{r}
ggplot(data=geneExp, aes(test_statistic)) +
  geom_histogram(bins=30)
```

>>>>

```{r, results='hide', message=FALSE}
# Load packages and source benchmark FDR
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)
library(R.utils)

@@

We'll create a plot to examine the distribution of effect sizes, since
the ash method assumes that the distribution of true (unobserved) effect
sizes is unimodal.

```{r}
ggplot(data=geneExp, aes(effect_size)) +
  geom_histogram(bins=30)
```

We'll also explore how the standard error (used by ash) 
correlates with the independent covariate (used by methods that incorporate 
covariates), in order to get an idea of how these pieces of information relate
to one another.

```{r}
ggplot(data=geneExp, aes(x = ind_covariate, y = SE)) +
  geom_hex(bins = 100) +
  scale_x_continuous(trans="log10") +
  xlab("Covariate: Mean gene expression") 
```
